Hybrid Threads for the Parrot Virtual Machine

### 2012-03-08 Paper.tex
Fix a typo
dukeleto++
Another typo
tadzik++

\nummer{1010307037-A}
\gegenstand{SWE}
\semester{Wintersemester 2012}
\betreuer{Dr. Heinz Dobler}
\license{This work is published under the conditions of the Createive Commons Attribution 3.0 Unported License (CC BY) -- see \url{http://creativecommons.org/licenses/by/3.0/}}

@@

In previous attempts to implement threading support in Parrot, the answer to this problem was to disable the garbage collector while multiple threads are active. Other VMs solve this problem by suspending all threads while the GC is running. While multithreaded garbage collection algorithms exist, their implementation would have been to complex and brittle for this paper\cite{VCGC}.

>>>>

\nummer{1010307037-A}
\gegenstand{SWE}
\semester{Wintersemester 2012}
\betreuer{Dr. Heinz Dobler}
\license{This work is published under the conditions of the Creative Commons Attribution 3.0 Unported License (CC BY) -- see \url{http://creativecommons.org/licenses/by/3.0/}}

@@

In previous attempts to implement threading support in Parrot, the answer to this problem was to disable the garbage collector while multiple threads are active. Other VMs solve this problem by suspending all threads while the GC is running. While multithreaded garbage collection algorithms exist, their implementation would have been too complex and brittle for this paper\cite{VCGC}.
